\begin{thebibliography}{99}

\bibitem{Optical properties of bialkali photocathodes}
D. Motta, S. Schonert
Optical properties of bialkali photocathodes
Nuclear Instruments and Methods in Physics Research A 539 (2005) 217–235

\bibitem{Qi_Li}
TOWARD A USER‘S TOOLKIT FOR MODELING SCINTILLATOR PROPORTIONALITY AND LIGHT YIELD

\bibitem{M.D. Lay}
M.D. Lay, Nucl. Instr. and Meth. A 383 (1996) 485;
M.D. Lay, M.J. Lyon, Nucl. Instr. and Meth. A 383 (1996)
495.

\bibitem{Light output and energy resolution}
Light output and energy resolution of $Lu_{0.7} Y_{0.3} AlO_{3}:Ce$ and $Lu_{1.95} Y_{0.05} SiO_{5}:Ce$ scintillators

\bibitem{Characterisation Studies of Silicon Photomultipliers}
Characterisation Studies of Silicon Photomultipliers
Patrick Eckert, Hans-Christian Schultz-Coulon, Wei Shen, Rainer Stamen, Alexander Tadday

\bibitem{Characterization and Simulation of the Response}
Characterization and Simulation of the Response of Multi Pixel Photon Counters to Low
Light Levels
A. Vacheretc, G.J. Barkerh
arXiv:1101.1996v1 [physics.ins-det] 11 Jan 2011

\bibitem{After-pulsingandcross-talkinmulti-pixelphotoncounters}
Y. Du, F. Retiere, Nucl. Instr. and Meth. A 596 (2008) 396-401

\bibitem{Modeling crosstalk in silicon photomultipliers}
Modeling crosstalk in silicon photomultipliers
L. Gallego, J. Rosado, F. Blanco and F. Arqueros

\bibitem{Silicon Photomultiplier's Gain Stabilization}
Silicon Photomultiplier's Gain Stabilization by Bias Correction for Compensation of the Temperature Fluctuations
P. Dorosz, M. Baszczyk, S. Glab, W. Kucewicz, L. Mik, M. Sapor

\bibitem{Temperature and Bias Voltage Dependence}
Temperature and Bias Voltage Dependence of the MPPC Detectors
N. Dinu, C. Bazin. V. Chaumat, C. Cheikali, A. Para, Member, IEEE, V. Puill, C. Sylvia, J.F. Vagnucci

\bibitem{Characterization of SiPM: temperature dependencies}
Characterization of SiPM: temperature dependencies.
Marco Ramilli

\bibitem{Characterisation of a silicon photomultiplier device}
Characterisation of a silicon photomultiplier device for applications in liquid argon based neutrino physics and dark matter searches
P.K. Lightfoot , G.J. Barker b, K. Mavrokoridis , Y.A. Ramachers , N.J.C. Spooner

\bibitem{Determination of the recovery time of silicon photomultipliers}
Determination of the recovery time of silicon photomultipliers
Parrick Hallen
Bachelor's thesis in physics

\end{thebibliography}

